A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-08-25 docs/introduction_v1.01.tex
Started writing data section.
Added short section on cored logarithmic halo.

\paragraph{SWELLS Survey}
\begin{itemize}
\item [TO DO]
\end{itemize}

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W ("blue")}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W ("red")}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000). Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e. assumes an angular diameter distance of 414 Mpc). The color scaling of these two images is the same. The black solid line in panel (a) shows the orientation of the major-axis. The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling. [TO DO: NOT ALL THE TIME.???????] \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted. An IRAF ellipse ???? fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G). \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc. The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$. [TO DO: Add (x,y) axis in figure b).???????]}
\label{fig:specialJ1331}
\end{figure*}

>>>>

\paragraph{SWELLS Survey}
\begin{itemize}
\item [TO DO]
\item \citet{SWELLSI} give measurements for the apparent AB magnitudes for the HST/WFPC2 I-band/F814W filter for disk and bulge, as well as stellar masses for stellar population models for a Chabrier [TO DO: REF] and Salpeter [TO DO: REF] initial mass function (IMF). 
\end{itemize}

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_450.ps}
  \caption{J1331 in F450W ("blue")}
  \label{fig:F450W}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/first_glimpse_814.ps}
  \caption{J1331 in F814W ("red")}
  \label{fig:F814W}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_imgpos.ps}
  \caption{The lensing images}
  \label{fig:lens_just_imgpos}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/stellar_kinematics_data.ps}
  \caption{Stellar Kinematics by \citet{SWELLSV}}
  \label{fig:kinematics}
\end{subfigure}
\caption{Hubble Space telescope (HST) images and stellar kinematics of the galaxy SDSS J1331+3638 (J1331), which has a large counter-rotating core and whose bulge acts as a strong lens for a bluish background source. \emph{Panel (a) and (b):} HST/WFPC2/WFC3 images of J1331 by \citet{SWELLSI} in two filters, F450W in panel (a) and F814W in panel (b). The galaxy's coordinates on the sky are right ascension $\alpha$ = 202.91800$^\circ$ and declination $\delta$ = 36.46999$^\circ$ (epoch J2000). Image orientation and scaling are indicated in panel (a); the scaling transformation from arcseconds to the physical size of the galaxy in kpc uses the galaxy's redshift $z_d = 0.113$ \citep{SWELLSIII} (i.e. assumes an angular diameter distance of 414 Mpc). The color scaling of these two images is the same. The black solid line in panel (b) shows the orientation of the major-axis. The line has a length of 10 arcsec and indicates the region within which we carry out the Jeans modelling. [TO DO: NOT ALL THE TIME.???????] \emph{Panel (c):} The central region of J1331 in F450W, surface brightness subtracted. An IRAF ellipse ???? fit to the F450W surface brightness in panel (a) was subtracted from the image. The (smoothed) residuals within the white square in panel (a) are shown in panel (c). Four bright blobs (A,B,C and D) become visible, which are arranged in a typical strong lensing configuration around the center of the galaxy (G). \emph{Panel (d):} Stellar Kinematics along the galaxy's major axis as measured by \citet{SWELLSV}, line-of-sight rotation velocity $v_\text{rot}$, line-of-sight velocity dispersion $\sigma$ and the rms-velocity $v_\text{rms} = \sqrt{v_\text{rot}^2 + \sigma^2}$. The dotted line in panel (b) indicates the galaxy's effective half-light radius (in the F814W filter), $R_\text{eff} = 2.6" = 5.2$ kpc. The $v_\text{rot}$ curve reveals that J1331 is counter-rotating within $R_\text{eff}$. [TO DO: Add (x,y) axis in figure b).???????]}
\label{fig:specialJ1331}
\end{figure*}

### 2015-08-25 docs/results_JAMwithNFW_v1.01.tex
Added short section on cored logarithmic halo.

\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC. Overplotted are also the priors used to constrain the NFW halo. The best fit parameters are summarized in Table \ref{tab:modelB4_bestfit}. We find that the best fit NFW halo strives to be more massive and with a higher concentration than  proposed by the prior. At the same time the model prefers again very negative velocity anisotropies; the sample with the highest probability is pegged at the lower limit of the prior. Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve. [TO DO: Rewrite. Not very good.]
The first panel in Figure \ref{fig:modelB4_vrot} shows the mean best fit values from Table \ref{tab:modelB4_bestfit}.

>>>>

\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC. Overplotted are also the priors used to constrain the NFW halo. The best fit parameters are summarized in Table \ref{tab:modelB4_bestfit}. We find that the best fit NFW halo strives to be more massive and with a higher concentration than  proposed by the prior. At the same time the model prefers again very negative velocity anisotropies; the sample with the highest probability is pegged at the lower limit of the prior. Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve. [TO DO: Rewrite. Not very good.]

The first panel in Figure \ref{fig:modelB4_vrot} shows the mean best fit values from Table \ref{tab:modelB4_bestfit}.

We also fitted a model with a cored logarithmic dark matter halo. The cored halo models are in general slightly less massive than the NFW halo and therefore fitt the outer regions of J1331 better. However, the density profile of the cored halo as well as the I-band light distribution within the plane drop as $\rho(r) \propto r^{-2}$, there is a strong degeneracy between the stellar mass and the dark matter. Overall we were not able to give tight constraints on the cored logarithmic halo.
